---
title: "Final Project"
author: "Yakub Rabiutheen"
desription: "Final Project"
date: "05/22/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
- Final Project
---


1. Identify an existing data set or collect your own data. Provide a thorough description of the network data and the protocols used to collect and code it. The information provided should be sufficient to allow someone to recreate your network data from the original source. 






First we will invoke the ipumsr library to read in the data. The read_ipums_micro() function takes two arguments: the DDI file and the data file. The DDI file is an XML file that contains metadata about the data. The data file is a gzipped file that contains the data itself. Both files are located in the posts/ directory.




```{r}
library(ipumsr)
ddi <- read_ipums_ddi("cps_00003.xml")
cps_data <- read_ipums_micro(ddi, data_file = "cps_00003.dat")
```




##Scraping IPUMS to get Industry Codes

Now I will scrape the IPUMS website to also get the Codes for each Industry for my IND column. 

```{markdown}
library(rvest)
library(dplyr)

# Base URL
base_url <- "https://cps.ipums.org"

# Page URL
page_url <- "https://cps.ipums.org/cps-action/variables/IND#codes_section"

# Read the HTML of the base page
main_page <- read_html(page_url)

# Find the links for different years
links <- main_page %>%
  html_nodes("a[href*='codes']") %>%
  html_attr("href")

# Correct the links (remove the 'https://cps.ipums.org' if it exists)
links <- gsub("https://cps.ipums.org", "", links)

# Create the full URLs
urls <- paste0(base_url, links)

# Initialize a list to hold the scraped data
data_list <- list()

# Loop through the URLs
for (url in urls) {
  # Read the HTML of the page
  page <- read_html(url)
  
  # Scrape the codes and descriptions
  dt <- page %>%
    html_nodes("dt") %>%
    html_text()
  dd <- page %>%
    html_nodes("dd") %>%
    html_text()
  
  # Combine the codes and descriptions into a data frame and add it to the list
  data_list[[url]] <- data.frame(Code = dt, Description = dd, stringsAsFactors = FALSE)
}

# Combine all the data frames into a single data frame
industry_codes <- bind_rows(data_list)

# View the data
print(industry_codes)
##Save Occupational Codes as CSV
write.csv(industry_codes, file = "industry_codes.csv")
```


Now let's read in Occupational Codes

```{r}
industry_codes<-read.csv("industry_codes.csv")
```



Adding Occupational Codes to IND Column
```{r}
cps_data$IND_1_Description <- industry_codes$Description[match(cps_data$IND_1, industry_codes$Code)]
cps_data$IND_1 <- NULL

# Replace numerical codes with descriptions in IND_2 column
cps_data$IND_2_Description <- industry_codes$Description[match(cps_data$IND_2, industry_codes$Code)]
cps_data$IND_2 <- NULL
```




Adding Race Labels to the Race Column
```{r}
levels <- c("100", "200", "300", "650", "651", "652", "700", "801", "802", "803", "804", "805", "806", "807", "808", "809", "810", "811", "812", "813", "814", "815", "816", "817", "818", "819", "820", "830")
labels <- c("White", "Black", "American Indian/Aleut/Eskimo", "Asian or Pacific Islander", "Asian only", "Hawaiian/Pacific Islander only", "Other (single) race, n.e.c.", "White-Black", "White-American Indian", "White-Asian", "White-Hawaiian/Pacific Islander", "Black-American Indian", "Black-Asian", "Black-Hawaiian/Pacific Islander", "American Indian-Asian", "Asian-Hawaiian/Pacific Islander", "White-Black-American Indian", "White-Black-Asian", "White-American Indian-Asian", "White-Asian-Hawaiian/Pacific Islander", "White-Black-American Indian-Asian", "American Indian-Hawaiian/Pacific Islander", "White-Black--Hawaiian/Pacific Islander", "White-American Indian-Hawaiian/Pacific Islander", "Black-American Indian-Asian", "White-American Indian-Asian-Hawaiian/Pacific Islander", "Two or three races, unspecified", "Four or five races, unspecified")

# Convert RACE_1 to a factor
cps_data$RACE_1 <- factor(cps_data$RACE_1, levels = levels, labels = labels)
```




```{r}
# Convert "SEX_1" to a factor with labels
cps_data$SEX_1 <- factor(cps_data$SEX_1, labels = c("Male", "Female"))
```



Adding Country labels to Country Column
Please note that the Census definees Country different from Race. Also, that the Census has historically asked about Country of Origin in different ways. For example, in 1970, the Census asked about Country of Origin for the first time. 

```{r}
# Define the labels for each country code
country_value <- c(10000, 10500, 11000, 11500, 12090, 15000, 16010, 19900, 20000, 21010, 21020, 21030, 21040, 21050, 21060, 21070, 21090, 25000, 26010, 26020, 26030, 26043, 26044, 26054, 26055, 26060, 26091, 30005, 30010, 30015, 30020, 30025, 30030, 30040, 30050, 30060, 30065, 30090, 40000, 40100, 40400, 40500, 41000, 41100, 41300, 41400, 41410, 42000, 42100, 42500, 42600, 43300, 43400, 43600, 43610, 43800, 45000, 45200, 45212, 45213, 45300, 45400, 45500, 45540, 45600, 45700, 46100, 46200, 46500, 46530, 46590, 49900, 50000, 50010, 50040, 50100, 50200, 50220, 51100, 51200, 51300, 51400, 51500, 51600, 51700, 51800, 52000, 52100, 52110, 52130, 52140, 52200, 53200, 53400, 53420, 53500, 53700, 54000, 54100, 54200, 54700, 59900, 60010, 60012, 60014, 60023, 60031, 60044, 60045, 60094, 60099, 70010, 70020, 71000, 71021, 96000)
country_label <- c( "American Samoa", "Guam", "Puerto Rico", "U.S. Virgin Islands", "U.S. outlying areas, n.s.", "Canada", "Bermuda", "North America, n.s.", "Mexico", "Belize/British Honduras", "Costa Rica", "El Salvador", "Guatemala", "Honduras", "Nicaragua", "Panama", "Central America, n.s.", "Cuba", "Dominican Republic", "Haiti", "Jamaica", "Bahamas", "Barbados", "Dominica", "Grenada", "Trinidad and Tobago", "Caribbean, n.s.", "Argentina", "Bolivia", "Brazil", "Chile", "Colombia", "Ecuador", "Guyana/British Guiana", "Peru", "Uruguay", "Venezuela", "South America, n.s.", "Denmark", "Finland", "Norway", "Sweden", "England", "Scotland", "United Kingdom, n.s.", "Ireland", "Northern Ireland", "Belgium", "France", "Netherlands", "Switzerland", "Greece", "Italy", "Portugal", "Azores", "Spain", "Austria", "Czechoslavakia", "Slovakia", "Czech Republic", "Germany", "Hungary", "Poland", "Armenia", "Romania", "Yugoslavia", "Latvia", "Lithuania", "Other USSR/Russia", "Ukraine", "USSR, n.s.", "Europe, n.s.", "China", "Hong Kong", "Taiwan", "Japan", "Korea", "South Korea", "Cambodia", "Indonesia", "Laos", "Malaysia", "Philippines", "Singapore", "Thailand", "Vietnam", "Afghanistan", "India", "Bangladesh", "Burma", "Pakistan", "Iran", "Iraq", "Israel/Palestine", "Palestine", "Jordan", "Lebanon", "Saudi Arabia", "Syria", "Turkey", "Middle East, n.s.", "Asia, n.e.c./n.s.", "Northern Africa", "Egypt/United Arab Rep.", "Morocco", "Ghana", "Nigeria", "Ethiopia", "Kenya", "South Africa (Union of)", "Africa, n.s./n.e.c.", "Australia", "New Zealand", "Pacific Islands", "Fiji", "Other, n.e.c. and unknown")

cps_data$COUNTRY_1 <- factor(cps_data$COUNTRY_1, levels = country_value, labels = country_label)           
```



```{r}
filtered_cps_data <- na.omit(cps_data[, c("COUNTRY_1", "IND_1_Description")])
```




```{r}
library(igraph)
edge_matrix_country <- data.frame(
  from = filtered_cps_data$COUNTRY_1,  # Replace with your actual column name for countries
  to = filtered_cps_data$IND_1_Description
)

g_country <- graph_from_data_frame(d = edge_matrix_country, directed = FALSE)
```


```{r}
summary(g_country)
```

```{r}
cat("Graph Summary:\n")
cat("Number of Nodes:", vcount(g_country), "\n")
cat("Number of Edges:", ecount(g_country), "\n")
cat("Diameter:", diameter(g_country), "\n")
```



```{r}
filtered_cps_data <- na.omit(cps_data[, c("RACE_1", "IND_1_Description")])

# Create the edge dataframe with proper column names
edge_matrix_race <- data.frame(
  from = filtered_cps_data$RACE_1,
  to = filtered_cps_data$IND_1_Description
)

# Convert the edge dataframe to an igraph object
g_race <- graph_from_data_frame(d = edge_matrix_race, directed = FALSE)
```






```{r}
# Edge list for Industry and Sex
filtered_cps_data <- na.omit(cps_data[, c("SEX_1", "IND_1_Description")])

# Create the edge dataframe with proper column names
edge_matrix_sex <- data.frame(
  from = filtered_cps_data$SEX_1,
  to = filtered_cps_data$IND_1_Description
)

# Convert the edge dataframe to an igraph object
g_sex <- graph_from_data_frame(d = edge_matrix_sex, directed = FALSE)
```







```{r}
library(igraph)
num_nodes_race <- vcount(g_race)
num_edges_race <- ecount(g_race)

num_nodes_sex <- vcount(g_sex)
num_edges_sex <- ecount(g_sex)

num_nodes_country <- vcount(g_country)
num_edges_country <- ecount(g_country)

# Diameter
diameter_race <- diameter(g_race)
diameter_sex <- diameter(g_sex)
diameter_country <- diameter(g_country)

# Degree centrality
degree_centrality_race <- degree(g_race)
degree_centrality_sex <- degree(g_sex)
degree_centrality_country <- degree(g_country)

# Betweenness centrality
betweenness_centrality_race <- betweenness(g_race)
betweenness_centrality_sex <- betweenness(g_sex)
betweenness_centrality_country <- betweenness(g_country)

# Eigenvector centrality
eigenvector_centrality_race <- eigen_centrality(g_race)$vector
eigenvector_centrality_sex <- eigen_centrality(g_sex)$vector
eigenvector_centrality_country <- eigen_centrality(g_country)$vector
```




```{r}
cat("Graph Summary:\n")

# Summary for g_race
cat("g_race\n")
cat("Number of Nodes:", vcount(g_race), "\n")
cat("Number of Edges:", ecount(g_race), "\n")
cat("Diameter:", diameter(g_race), "\n")

# Summary for g_country
cat("g_country\n")
cat("Number of Nodes:", vcount(g_country), "\n")
cat("Number of Edges:", ecount(g_country), "\n")
cat("Diameter:", diameter(g_country), "\n")

# Summary for g_sex
cat("g_sex\n")
cat("Number of Nodes:", vcount(g_sex), "\n")
cat("Number of Edges:", ecount(g_sex), "\n")
cat("Diameter:", diameter(g_sex), "\n")
```








##Answers to Question 1##

a.Where is the data set from, and what is being measured? Was the original data in matrix, edgelist or affiliation network format?


The data that I will be using is Data from  Current Population Survey provided by Integrated Public Use Microdata Series(IPUMS) which was created by University Of Minessota.

The Current Population Survey originally comes from the Bureau of Labor,and IPUMS is a data aggregator that harmonized the CPS  Data creating consistent variables across years to facilitate longitudinal analysis.


b.Is this network a sample or does it represent the universe of cases? If a sample, is the sample adequate/random/suitable?

The Data is  a sample collected by the Bureau of Labor Statistics. The sample is adequate and suitable because it is a random sample of the population.

Also, the CPS dataset is designed to answer questions regarding Labor Force Demographics.


c. What constitutes a vertex/node in these data? What is the level of analysis (person, organization, etc.)? How many nodes are in the data set?

The level are analaysis are people. Each node represents a person responding to the survey. The edges represent a connection of industry to their self reported race, gender or country of origin in the Census.



In terms of the the numbers of nodes, it varies  by each graph.

g_race
Number of Nodes: 567 
Number of Edges: 2058407 
Diameter: 3 
g_country
Number of Nodes: 296 
Number of Edges: 1548 
Diameter: 7 
g_sex
Number of Nodes: 541 
Number of Edges: 2058407 
Diameter: 4 



d.What constitutes a tie in these data? Is the tie weighted or unweighted? If weighted, what is the range of tie values? What is the tie measuring, and is the measure adequate?

The Tie that this Data is measuring is the tie between the Industry a Person is in and the Demographic variables that a person has such as Race, Coutnry of Origin and  Gender.



e.
Were any transformations used (e.g., thresholds, one-mode projection) to create final network data used in analysis?

There were no transformations suhc as thresholds or one-mode projection used to create the final network data used in analysis.






##Answers to Question 2

2.

Provide additional descriptive statistics about your network data. The information provided should be sufficient to allow someone to understand the distinctive features of your network data. Please include a substantive discussion or interpretation of the meaning of each of these features – this is not merely a statistical report. In addition to basic information about network size and range of tie values (provided above), look at the following:
number of components
(if not fully connected) proportion of nodes in giant component and proportion of unconnected nodes/singletons (if any)
(fully connected graphs or subgraphs only) Network diameter (the length of the longest geodesic in the network). Maybe distribution of network geodesics.
graph density
average node degree and degree distribution





a. number of components
```{r}
components_sex <- decompose.graph(g_sex)
components_race <- decompose.graph(g_race)
components_country <- decompose.graph(g_country)

# Number of Components
cat("Number of Components:\n")
cat("g_sex:", length(components_sex), "\n")
cat("g_race:", length(components_race), "\n")
cat("g_country:", length(components_country), "\n\n")

```
Number of Components:
g_sex: 1 
g_race: 1 
g_country: 2 

For Gender and Race, all the Nodes are Connected either directly or by some path.

In contrast, the Country networkgraph is divided into two separate parts, with no connections between them.




b.(if not fully connected) proportion of nodes in giant component and proportion of unconnected nodes/singletons (if any)
```{r}
g_sex_simple <- simplify(g_sex)
g_race_simple <- simplify(g_race)
g_country_simple <- simplify(g_country)

# Detect communities
communities_sex <- cluster_fast_greedy(g_sex_simple)
communities_race <- cluster_fast_greedy(g_race_simple)
communities_country <- cluster_fast_greedy(g_country_simple)
sizes_sex <- sizes(communities_sex)
sizes_race <- sizes(communities_race)
sizes_country <- sizes(communities_country)
prop_giant_comp_sex <- max(sizes_sex) / vcount(g_sex_simple)
prop_giant_comp_race <- max(sizes_race) / vcount(g_race_simple)
prop_giant_comp_country <- max(sizes_country) / vcount(g_country_simple)
cat("Proportion of Nodes in Giant Component:\n")
cat("g_sex:", prop_giant_comp_sex, "\n")
cat("g_race:", prop_giant_comp_race, "\n")
cat("g_country:", prop_giant_comp_country, "\n\n")
```
g_sex: 0.5009242 
g_race: 0.5837743 
g_country: 0.1790541 


g_sex: 0.5009242: About 50.09% of the nodes in the g_sex graph are part of the largest connected component.

g_race: 0.5837743: About 58.38% of the nodes in the g_race graph are part of the largest connected component.

g_country: 0.1790541: Only about 17.91% of the nodes in the g_country graph are part of the largest connected component.


C.(fully connected graphs or subgraphs only) Network diameter (the length of the longest geodesic in the network). Maybe distribution of network geodesics.

```{r}
##Diameter
cat("Diameter:", diameter(g_race), "\n")
cat("Diameter:", diameter(g_country), "\n")
cat("Diameter:", diameter(g_sex), "\n")
```
 g_race: Diameter: 3 
g_country: Diameter: 7 
g_sex: Diameter: 4 




D.graph density
```{r}
# Network Density
density_sex <- edge_density(g_sex)
density_race <- edge_density(g_race)
density_country <- edge_density(g_country)
cat("Network Density:\n")
cat("g_sex:", density_sex, "\n")
cat("g_race:", density_race, "\n")
cat("g_country:", density_country, "\n\n")
```
Network Density:
g_sex: 14.09192 
g_race: 12.82808 
g_country: 0.03545579 



e.average node degree and degree distribution
```{r}
avg_degree_sex <- mean(degree(g_sex))
avg_degree_race <- mean(degree(g_race))
avg_degree_country <- mean(degree(g_country))
cat("Average Node Degree:\n")
cat("g_sex:", avg_degree_sex, "\n")
cat("g_race:", avg_degree_race, "\n")
cat("g_country:", avg_degree_country, "\n\n")
```
Average Node Degree:
g_sex: 7609.638 
g_race: 7260.695 
g_country: 10.45946 



```{r}
cat("Degree Distribution Summary:\n")
cat("g_sex:\n")
summary(degree_distribution(g_sex))

cat("\ng_race:\n")
summary(degree_distribution(g_race))

cat("\ng_country:\n")
summary(degree_distribution(g_country))
```


3.Provide a visualization of the network. If the network is too large to be anything more than a hairball, visualize a subset of the graph with a rationale for selecting that subset 

Visualization for g_race
```{r}
library(igraph)
subset_vertices <- sample(V(g_race), size = 20)

# Get the labels of the selected races
labels <- V(g_race)$RACE_1[subset_vertices]

# Create a subgraph containing only the subset of vertices and their incident edges
subgraph_race <- induced_subgraph(g_race, subset_vertices)

# Plot the subgraph with vertex labels and edges
plot(subgraph_race, vertex.label = labels, edge.arrow.size = 0.5)
```

Visualization for g_sex
```{r}
subset_vertices <- sample(V(g_sex), size = 20)

# Get the labels of the selected sexes
labels <- V(g_sex)$SEX_1[subset_vertices]

# Create a subgraph containing only the subset of vertices and their incident edges
subgraph_sex <- induced_subgraph(g_sex, subset_vertices)

# Plot the subgraph with vertex labels and edges
plot(subgraph_sex, vertex.label = labels, edge.arrow.size = 0.5)
```


Visualization for g_country
```{r}
subset_vertices <- sample(V(g_country), size = 20)

# Get the labels of the selected countries
labels <- V(g_country)$COUNTRY_1[subset_vertices]

# Create a subgraph containing only the subset of vertices and their incident edges
subgraph_country <- induced_subgraph(g_country, subset_vertices)

# Plot the subgraph with vertex labels and edges
plot(subgraph_country, vertex.label = labels, edge.arrow.size = 0.5)

```



3. Identify prominent nodes in the graph using at least one from each group of measures (a and b) below and interpret your results. 

a. Measures of popularity/status: degree centrality, betweenness centrality, eigenvector centrality

b.Measures of role/power: structural equivalence (use a similarity measure from week 6), constraint, betweenness, Gould/Fernandez brokerage.

Measures for a & b for all three graphs.


g_sex
```{r}
# Calculate measures of popularity/status
degree_centrality_sex <- degree(g_sex)
betweenness_centrality <- betweenness(g_sex)
eigenvector_centrality <- eigen_centrality(g_sex)$vector

# Print the measures of popularity/status
cat("Centrality Measures for Gender\n")

# In-degree
cat("Degree Centrality :\n")
print(head(sort(degree_centrality_sex , decreasing = TRUE), n = 10))

# Betweenness centrality
cat("\nBetweenness Centrality:\n")
print(head(sort(betweenness_centrality, decreasing = TRUE), n = 10))

# Eigenvector centrality
cat("\nEigenvector Centrality:\n")
print(head(sort(eigenvector_centrality, decreasing = TRUE), n = 10))
```




```{r}
##Race
degree_centrality_race <- degree(g_race)
betweenness_centrality_race <- betweenness(g_race)
eigenvector_centrality_race <- eigen_centrality(g_race)$vector
cat("Degree Centrality For Race:\n")
print(head(sort(degree_centrality_race , decreasing = TRUE), n = 10))
cat("\nBetweenness Centrality for Race :\n")
print(head(sort(betweenness_centrality_race, decreasing = TRUE), n = 10))
cat("\nEigenvector Centrality For Race:\n")
print(head(sort(eigenvector_centrality_race, decreasing = TRUE), n = 10))
```


```{r}
degree_centrality_country <- degree(g_country)
betweenness_centrality_country <- betweenness(g_country)
eigenvector_centrality_country <- eigen_centrality(g_country)$vector

cat("Degree Centrality for Country:\n")
print(head(sort(degree_centrality_country, decreasing = TRUE), n = 10))

cat("\nBetweenness Centrality for Country:\n")
print(head(sort(betweenness_centrality_country, decreasing = TRUE), n = 10))

cat("\nEigenvector Centrality for Country:\n")
print(head(sort(eigenvector_centrality_country, decreasing = TRUE), n = 10))
```



## Filtering Graphs to identify Industries domianted by Race and Gender

c.Clearly define the measure that you are using and explain what being high/low on the measure indicates

I'm going to filter Degree Centrality of White among Race and  Male among Sex to see industries domianted by White Males.

```{r}
filtered_edges <- edge_matrix_race[edge_matrix_race$from == "White", ]

# Create a new igraph object with the filtered edges
g_white <- graph_from_data_frame(filtered_edges, directed = FALSE)

eigenvector_centrality_white <- eigen_centrality(g_white)$vector
print(head(sort(eigenvector_centrality_white[-1], decreasing = TRUE), n = 10))
```

```{r}
filtered_edges <- edge_matrix_sex[edge_matrix_sex$from == "Male", ]
g_male <- graph_from_data_frame(filtered_edges, directed = FALSE)
eigenvector_centrality_male <- eigen_centrality(g_male)$vector
print(head(sort(eigenvector_centrality_male[-1], decreasing = TRUE), n = 10))
```

e.Identify the node(s) that have remarkable (high/low/higher/lower than expected) values on the measure in question.

One thing that I found suprising was that the eigenvector Industries for "White" and "Male" were similar.

Another thing I didn't expect was that Hospitals were Male Dominated. Perhaps, that is due to Hospital Management being male-lead.

f.What sort of expectations do we have for the behavior of the node(s) identified, and does their observed behavior fulfill these expectations?

One thing that I found interesting was that the Men had the highest betweenness centrality, showing they control the flow of connections between Industries. 
```{r}
# Louvain algorithm for community detection
louvain_race <- cluster_louvain(g_race)
louvain_country <- cluster_louvain(g_country)
louvain_sex <- cluster_louvain(g_sex)

# Community membership
community_race <- membership(louvain_race)
community_country <- membership(louvain_country)
community_sex <- membership(louvain_sex)
```


For Loop for Communities among g_race
```{r}
for (i in unique(community_race)) {
  cat("Community", i, ": ")
  vertices <- V(g_race)$name[community_race == i]
  print(vertices)
}
```

For Loop for Communities among g_sex
```{r}
for (i in unique(community_sex)) {
  cat("Community", i, ": ")
  vertices <- V(g_sex)$name[community_sex == i]
  print(vertices)
}
```


For Loop for Communities among g_country
```{r}
for (i in unique(community_country)) {
  cat("Community", i, ": ")
  vertices <- V(g_country)$name[community_country == i]
  print(vertices)
}
```





 
 
 
 6. Identify at least one network-related hypothesis that might be asked using these network data and use inferential statistics to address this question



```{r}
library(network)
edges_gender <- as_edgelist(g_sex)
network_gender <- network(edges_gender)
```


#Hypopthesis , Increased Edges for Gender and Race result in Negative Coefficient or less desirable Outcomes for Networks.

As it basically, leaves Industries open to divide and Conquer.

```{r}
library(ergm)
model_gender <- ergm(network_gender ~ edges)
summary(model_gender)
```
The estimated coefficient for the edges term is -4.41290, with a standard error of 0.01623. The negative coefficient suggests that the presence of edges (connections) in the gender network has a significant negative effect.

The AIC  is 41652, and the BIC  is 41663. . The AIC and BIC values are quite close, indicating a good fit of the model.



```{r}
num_edges_race <- as_edgelist(g_race)
network_race <- network(num_edges_race)
erg_race <- ergm(network_race ~ edges)
summary(erg_race)
```

The estimated coefficient for the edges term is -4.41290, with a standard error of 0.01623. The negative coefficient suggests that the presence of edges (connections) in the race network has a significant negative effect.

The AIC  is 41652, and the BIC  is 41663.The AIC and BIC values are quite close, indicating a good fit of the model.




```{r}
num_edges_country <- as_edgelist(g_country)
network_country <- network(num_edges_country )
erg_race <- ergm(network_country  ~ edges)
summary(erg_race)
```

Again another negative coefficient, suggesting that the presence of edges (connections) in the country network has a significant negative effect.

The AIC  is 7412, and the BIC  is 7422. The AIC and BIC values are quite close, indicating a good fit of the model.