---
title: "Week 4 Challenge Instructions"
author: "Yakub Rabiuhteen"
description: "Centrality of a Network"
date: "03/06/2023"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
# editor: visual
categories: 
  - challenge_4
  - instructions
  # - railroads
  # - faostat
  # - wildbirds
---
## Challenge Overview

Describe the many measures of centrality of at least one network of your choice.

I have decided to use the Florentine Dataset.
```{r}
library(tidyverse)
library(igraph)
library(sna)
library(network)
library(statnet)
```



```{r}
data(flo)
```

## Describe the Network Data

If you have not done it before, always start by evaluating the basic structure of the network (number of edges and vertices, dyad and triad census, etc.). Create a data frame `nodes` with the corresponding local attributes such as degree or local transitivity.


```{r}
flo_net <- network(flo, directed = FALSE)
```

```{r}
network(flo_net, directed = FALSE)
```

 Network attributes:
  vertices = 16 
  directed = FALSE 
  hyper = FALSE 
  loops = FALSE 
  multiple = FALSE 
  bipartite = FALSE 
  total edges= 20 
    missing edges= 0 
    non-missing edges= 20 

There are 16 actors and 20 ties in the network.

It is not directed or a bipariate network.




```{r}
vertex_names <- network.vertex.names(flo_net)
```

 [1] "Acciaiuoli"   "Albizzi"      "Barbadori"    "Bischeri"     "Castellani"   "Ginori"       "Guadagni"     "Lamberteschi" "Medici"      
[10] "Pazzi"        "Peruzzi"      "Pucci"        "Ridolfi"      "Salviati"     "Strozzi"      "Tornabuoni"  


```{r}
network.vertex.names(flo_net) <- network.vertex.names(flo_net)
```



use igraph to plot the network
```{r}
florentine_igraph <- graph_from_data_frame(flo_net, directed = FALSE)
```

```{r}
plot(florentine_igraph, vertex.label = vertex_names)
```

## Centrality

Compute at least one measure of centrality for each node, adding them as attributes to `nodes` in the form of extra columns: eigencentrality, betweenness, closeness, etc. Compute the distribution of at least one of those measures. What do we learn from comparing these measures of centrality with an equivalent random network (i.e. with the same number of edges and vertices)?




```{r}
# Compute Indegree Measures
totdegree <- igraph::degree(florentine_igraph)
indegree <- igraph::degree(florentine_igraph, mode = "in", loops = FALSE)
outdegree <- igraph::degree(florentine_igraph, mode = "out", loops = FALSE)
globtrans <- igraph::transitivity(florentine_igraph, type = "global")
avgtrans <- igraph::transitivity(florentine_igraph, type = "average")
#Compute Centerality Measures
eigencentrality <- igraph::eigen_centrality(florentine_igraph)$vector
betweenness <- igraph::betweenness(florentine_igraph)
closeness <- igraph::closeness(florentine_igraph)
#Add Centerality Atribbutes to the nodes
florentine_igraph_nodes$totdegree <- totdegree
florentine_igraph_nodes$indegree <- indegree
florentine_igraph_nodes$outdegree <- outdegree
florentine_igraph_nodes$globtrans <- globtrans
florentine_igraph_nodes$avgtrans <- avgtrans
florentine_igraph_nodes$eigencentrality <- eigencentrality
florentine_igraph_nodes$betweenness <- betweenness
florentine_igraph_nodes$closeness <- closeness
```

```{r}
florentine_igraph_nodes
```

Here are some observations:
- "Medici" stands out as the most central node in the network with the highest scores across multiple centrality measures:
  - Total degree: 6
  - Indegree: 6
  - Outdegree: 6
  - Global transitivity: 0.1914894
  - Average transitivity: 0.2181818
  - Eigencentrality: 1.0000000
  - Betweenness: 47.500000
  - Closeness: 0.04000000

- Nodes "Ginori," "Lamberteschi," "Acciaiuoli," and "Pazzi" exhibit relatively lower centrality scores compared to others in the network:
  - Total degree: 1
  - Indegree: 1
  - Outdegree: 1
  - Global transitivity: 0.1914894
  - Average transitivity: 0.2181818
  - Eigencentrality: 0.1741141
  - Betweenness: 0.000000
  - Closeness: 0.02380952

- Nodes "Guadagni," "Strozzi," "Ridolfi," and "Albizzi" show higher centrality scores, indicating their significant roles within the network:
  - Total degree: 4
  - Indegree: 4
  - Outdegree: 4
  - Global transitivity: 0.1914894
  - Average transitivity: 0.2181818
  - Eigencentrality: 0.6718805 (Guadagni), 0.8272688 (Strozzi), 0.7937398 (Ridolfi), 0.5669336 (Albizzi)
  - Betweenness: 23.166667 (Guadagni), 9.333333 (Strozzi), 10.333333 (Ridolfi), 19.333333 (Albizzi)
  - Closeness: 0.03333333 (Guadagni), 0.03125000 (Strozzi), 0.03571429 (Ridolfi), 0.03448276 (Albizzi)











